The value of being indispensable: a cooperative approach to bargaining with a continuum of players

### 2024-02-09 src/paper/theory.tex
Prove the main theorem

\subsection{Weighted values}

@@

    Now let us condition this probability distriibution on the draw of player $P$:
    \begin{align*}
        [X_n]_l < x \mid U_P = u = \frac{1}{n} \sum_{i=1}^n \mathbf{1}[U_{li} < u].
    \end{align*}
    As the draws are independent, by the strong law of large numbers,
    \begin{align*}
        [X_n]_l < x \mid U_P \xrightarrow[a.s.]{} \E[\mathbf{1}[U_{li} < u]] = u.
    \end{align*}

    Now we can use \cref{lem:convergence_to_manifold} to conclude that $X_n \xrightarrow[]{d} (U, \dots, U)$.
    Finally, by \cref{lem:many_sided_manifold}, the Shapley-value is
    \begin{align*}
        \varphi_P^\infty & = \int_0^1 f(t, \dots, t) \dt.
    \end{align*}

@@

\begin{proof}[Proof of \cref{prop:many_sided_weighted}]
    The proof uses the same approach as that of \cref{prop:many_sided_shapley}.
    I will show that $X_n \xrightarrow[]{d} h(\xi)$, where $h(s) = (s^{\lambda_1}, \dots, s^{\lambda_L})$, and $\xi$ is a random variable with cdf $G(s) = s^{\lambda_P}$, and then rely on \cref{lem:many_sided_manifold}.

>>>>

\subsection{Weighted values}
\label{sec:weighted_one_sided}

@@

    Now let us condition this probability distribution on the draw of player $P$:
    \begin{align*}
        [X_n]_l < x \mid U_P = u = \frac{1}{n} \sum_{i=1}^n \mathbf{1}[U_{li} < u].
    \end{align*}
    As the draws are independent, by the strong law of large numbers,
    \begin{align*}
        [X_n]_l < x \mid U_P \xrightarrow[]{a.s.} \E[\mathbf{1}[U_{li} < u]] = u.
    \end{align*}

    Now we can use \cref{lem:convergence_to_manifold} to conclude that $X_n \xrightarrow[]{d} (U, \dots, U)$.
    Finally, by \cref{lem:many_sided_manifold}, the Shapley-value is
    \begin{align*}
        \varphi_P^\infty & = \int_0^1 f(s, \dots, s) \dt
    \end{align*}
    and the value of fringe $l$ is
    \begin{align*}
        \varphi_{A_l}^\infty & = \int_0^1 \partial_l f(s, \dots, s) \ds
    \end{align*}

@@

\begin{proof}[Proof of \cref{prop:many_sided_weighted}]
    The proof uses the same approach as that of \cref{prop:many_sided_shapley}.
    I will show that $X_n \xrightarrow[]{d} h(S)$, where $h(s) = (s^{\lambda_1}, \dots, s^{\lambda_L})$, and $S$ is a random variable with cdf $G(s) = s^{\lambda_P}$, and then rely on \cref{lem:many_sided_manifold}.

    First, as before, let us characterize the probabilities of the various permutations.
    The approach I am using relies on two main ideas.

    First, as shown by \textcite{kalai1987weighted}, the probability of a permutation can be described by successively selecting the players with probabilities proportional to the weights of the players that have not been selected yet, and then reversing this ordering.\footnote{
        For more details, see \cref{sec:weighted_one_sided}.
    }

    The other key result I rely on is the main proposition of \textcite{efraimidis2006weighted}.
    It states that weighted random sampling without replacement can be also be achieved by the following procedure.
    First, for each player $i$, draw a random number from the distribution $U^{\frac{1}{\lambda_i}}$, where $U$ is uniformly distributed on $[0, 1]$, and $\lambda_i$ is the sampling weight of player $i$.
    Then, for a sample size of $m$, select the $m$ players with the largest numbers.

    An immediate corollary of the latter result is that the procedure described by \textcite{kalai1987weighted} is equivalent to the following procedure.
    First, for each player $i$, draw a random number from the distribution $V_i = U^{\frac{1}{\lambda_i}}$, where $U$ is uniformly distributed on $[0, 1]$.
    Then, for each player $i$, sort the players according to the drawn numbers in ascending order.

    Now let us characterize $X_n$ in terms of this procedure.
    $[X_n]_l$ is the proportion of players of type $A_l$ that are placed before player $P$, or, equivalently, the number of players of type $A_l$ that have drawn a number less than player $P$.
    I.e.,
    \begin{align*}
        [X_n]_l = \frac{1}{n}\sum_{i = 1}^n \mathbf{1}[V_{li} < V_P].
    \end{align*}

    Now let us condition this probability distribution on the draw of player $P$:
    \begin{align*}
        [X_n]_l < x \mid V_P = s = \frac{1}{n} \sum_{i=1}^n \mathbf{1}[V_{li} < u].
    \end{align*}
    Then use the strong law of large numbers to deduce that
    \begin{align*}
        [X_n]_l < x \mid V_P \xrightarrow[]{a.s.} \E[\mathbf{1}[V_{li} < u]] = u^{\lambda_l}.
    \end{align*}
    Then we can rely on \cref{lem:convergence_to_manifold} to conclude that $X_n \xrightarrow[]{d} (V_P^{\lambda_1}, \dots, V_P^{\lambda_L})$.

    Finally, by \cref{lem:many_sided_manifold}, the weighted value of player $P$ is
    \begin{align*}
        \varphi_P^\infty &= \int_0^1 f(s_1^{\lambda_1}, \dots, s_L^{\lambda_L}) \mathrm{d} V_P(s) \\
        &= \int_0^1 f(s_1^{\lambda_1}, \dots, s_L^{\lambda_L}) \lambda_P s^{\lambda_P - 1} \ds,
    \end{align*}
    and the value of fringe $l$ is
    \begin{align*}
        \varphi_{A_l}^\infty &= \int_0^1 t^{\lambda_P} \lambda_l s^{\lambda_l - 1} \partial_l f(s_1^{\lambda_1}, \dots, s_L^{\lambda_L}) \lambda_P s^{\lambda_P - 1} \ds.
    \end{align*}
